---
title: "Untitled"
author: "Vinoth Aryan Nagabosshanam"
date: "March 20, 2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
# load package 'readxl' to load data from xlsx file

```{r}
library(MASS)
#install.packages("ISLR")
library(ISLR)

```

** now we are going to import the boston Data **

```{r}
# to colums name by using following
colnames(Boston)
str(Boston)
```

# Data Description of Boston dataset
Description
The Boston data frame has 506 rows and 14 columns.
This data frame contains the following columns:
**crim == per capita crime rate by town.**
**zn**=proportion of residential land zoned for lots over 25,000 sq.ft.
**indus**==proportion of non-retail business acres per town.
**chas**=Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
**nox**==nitrogen oxides concentration (parts per 10 million).
**rm**==average number of rooms per dwelling.
**age**==proportion of owner-occupied units built prior to 1940.
**dis**==weighted mean of distances to five Boston employment centres.
**rad**==index of accessibility to radial highways.
**tax**==full-value property-tax rate per \$10,000.
**ptratio**==pupil-teacher ratio by town.
**black**==1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.
**lstat**==lower status of the population (percent).
**medv**==median value of owner-occupied homes in \$1000s.

# Creat a simple linear regression 
** as the the rule weare now selecting the subset based on the value we will selset the the best subset**
```{r}
plot(medv~lstat,Boston)
fit1=lm(medv~lstat,data=Boston)
fit1
summary(fit1)

names(fit1)
confint(fit1)

predict(fit1,data.frame(lstat=c(5,10,15)),interval="confidence")

```

## multiple linear  regresssion
```{r}
fit2=lm(medv~lstat+age,data=Boston)
summary(fit2)
```

# now we are create mutiple linear regression model whith all variable 
```{r}
all_fit<-lm(medv~.,data = Boston)
summary(all_fit)

par(mfrow=c(2,2))
plot(all_fit)
```

after see the p value of age and idus it look so high so we are those two variable and crerating a new model

# now create the final multiple linear regression model 
```{r}
final_fit<-lm(medv~.-age-indus,data=Boston)
summary(final_fit)
par(mfrow=c(2,2))
plot(final_fit)
```

## ### Nonlinear terms and Interactions
```{r}
fit5=lm(medv~lstat*age,Boston)
summary(fit5)
fit6=lm(medv~lstat +I(lstat^2),Boston)
summary(fit6)
attach(Boston)

par(mfrow=c(1,1))
plot(medv~lstat)
points(lstat,fitted(fit6),col="red",pch=20)
fit7=lm(medv~poly(lstat,4))
points(lstat,fitted(fit7),col="blue",pch=20)
plot(1:20,1:20,pch=1:20,cex=2)
```

###Qualitative predictors

```{r}
# fix(Carseats)
names(Carseats)
summary(Carseats)
fit1=lm(Sales~.+Income:Advertising+Age:Price,Carseats)
summary(fit1)
par(mfrow=c(2,2))
plot(fit1)
contrasts(Carseats$ShelveLoc)
###Writing R functions
regplot=function(x,y){
  fit=lm(y~x)
  plot(x,y)
  abline(fit,col="red")
}

regplot(Carseats$Price,Carseats$Sales)
```

